quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-08 paper-quollr.Rmd
Updated detourr link plots

error_plt <- ggplotly(error_plt, width = 400,
                      height = 400, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)

@@

nldr_plt <- ggplotly(nldr_plt, width = 400,
                     height = 400, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)
```

@@

detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "500px", height = "500px")

erlndet_link <- crosstalk::bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr 1fr;",
    error_plt, 
    nldr_plt,
    htmltools::div(style = "margin-top: 20px;", detourr_output)
  ),
  device = "xs"
)

>>>>

error_plt <- ggplotly(error_plt, width = 200,
                      height = 200, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)

@@

nldr_plt <- ggplotly(nldr_plt, width = 200,
                     height = 200, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)
```

@@

detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "200px", height = "200px")

erlndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
        error_plt, 
        nldr_plt, 
    htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)

### 2025-12-08 paper-quollr.tex
Updated detourr link plots

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "500px", height = "500px")

erlndet_link <- crosstalk::bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr 1fr;",
    error_plt, 
    nldr_plt,
    htmltools::div(style = "margin-top: 20px;", detourr_output)
  ),
  device = "xs"
)

>>>>

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "200px", height = "200px")

erlndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
        error_plt, 
        nldr_plt, 
    htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)
